% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TEX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVTitle}{Stephen D. O'Connell}
\newcommand{\CVNote}{CV prepared on {\today}.}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={Stephen D. O'Connell},
pdfsubject={http://www.stephenoconnell.org},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

\usepackage{multicol}
\usepackage{changepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%
\vspace*{-1.5cm}

{\Large Stephen D. O'Connell}

{\normalsize
\par
\href{mailto:soconnell@emory.edu}
{soconnell@emory.edu}
}
\\
\href{http://www.stephenoconnell.org}
{www.stephenoconnell.org}
}

\begin{body}

\bigskip

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%
\vspace{-1cm}
\section
{Current}
{Current}
{PDF:Employment}

\href{http://economics.emory.edu/home/index.html}
{\textbf{Emory University, Department of Economics}}

\SmallEntryGap
Assistant Professor 
\hfill
\DatestampYMD{2018}{8}{} - Present


\section
{Previous}
{Previous}
{PDF:Employment}

\href{https://seii.mit.edu/}
{\textbf{Massachusetts Institute of Technology, Department of Economics and SEII}}

\SmallEntryGap
Postdoctoral Fellow
\hfill
\DatestampYMD{2016}{7}{} - \DatestampYMD{2018}{6}{}

\section
{Education}
{Education}
{PDF:Education}

\href{http://www.gc.cuny.edu/economics}
{\textbf{The Graduate Center at City University of New York}}

\SmallEntryGap
Doctor of Philosophy (Ph.D.) in
Economics
\hfill
\DatestampYMD{2016}{6}{}

\SmallEntryGap
Master of Philosophy (M.Phil.) in Economics
\hfill
\DatestampYMD{2013}{09}{}

\BigEntryGap
\textbf{Boston College}
\par
Bachelor of Arts (B.A.) in
Economics
\hfill
\DatestampYMD{2007}{05}{}

%%%%%%%%%%%%%%%
\section
{Affiliations}
{Affiliations}
{PDF:Affiliations}

\SmallEntryGap
\textbf{Emory University, Department of Quantitative Theory \& Methods}
\hfill
\DatestampYMD{2019}{8}{} - Present

Faculty Affiliate

\BigEntryGap

\SmallEntryGap
\textbf{IZA Institute of Labor Economics}
\hfill
\DatestampYMD{2015}{12}{} - present

Research Affiliate

%\BigEntryGap
%\href{www.javeriana.edu.co}
%{\textbf{Pontificia Universidad Javeriana, Bogot\'{a}}}
%\hfill
%Summer, 2016
%
%Visiting Faculty

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section
{Research}
{Research}
{PDF:Research}


\subsection
{Peer-reviewed articles}
{Journals}
{PDF:Journals}

\EntryGapNoBreak
\href{https://www.mitpressjournals.org/doi/pdf/10.1162/rest_a_00802}
{Stephen D. O'Connell, ``Can quotas increase the supply of candidates for higher-level positions? Evidence from local government in India,'' \textit{Forthcoming, Review of Economics and Statistics.}}

\EntryGapNoBreak
\href{https://doi.org/10.1016/j.jdeveco.2018.08.004}
{Stephen D. O'Connell, ``Political inclusion and educational investment: Estimates from a national policy experiment in India,''
\textit{Journal of Development Economics}, vol.~135, pp.~478-487, \datestampYM{2018}{} }


%\EntryGapNoBreak
%\href{https://www.tandfonline.com/doi/abs/10.1080/15391523.2017.1408438}
%{Stephen D. O'Connell and Guido Lang, ``Can Personalized Nudges Improve Learning in Hybrid Classes? Experimental Evidence From an Introductory Undergraduate Course,'' \textit{Journal of Research on Technology in Education}, vol.~50 no.~2, pp.~105-119, \datestampYM{2018}{}.}


\EntryGapNoBreak
\href{http://www.stephenoconnell.org/files/DPRTjpam_final.pdf}
{Theodore Joyce, Dahlia Remler, David Jaeger, Onur Altındağ, Stephen D. O'Connell and Sean Crockett,
``On Measuring and Reducing Selection Bias with a Quasi-Doubly Randomized Preference Trial,''
\textit{Journal of Policy Analysis and Management},
vol.~36,
no.~2,
pp.~438--459,
\DatestampYM{2017}{}.}

\EntryGapNoBreak
\href{http://www.stephenoconnell.org/files/ACWO2016_AER_Shortages.pdf}
{Hunt Allcott, Allan Collard-Wexler, and Stephen D. O'Connell,
``How Do Electricity Shortages Affect Industry? Evidence from India,''
\textit{American Economic Review},
vol.~106,
no.~3,
pp.~587--624,
\DatestampYM{2016}{}.}

\EntryGapNoBreak
\href{http://www.djaeger.org/research/pubs/EER_forthcoming.pdf}
{Theodore J. Joyce, Sean Crockett, David A. Jaeger, Onur Altindag and Stephen D. O'Connell,
``Does Classroom Time Matter?''
\textit{Economics of Education Review},
vol.~46
pp.~64-77,
\DatestampYM{2015}{}.}

%\EntryGapNoBreak
%\href{http://isedj.org/2015-13/n1/ISEDJv13n1p14.pdf}
%{Stephen D. O'Connell and Guido Lang, ``Learning Styles, Online Content Usage and Exam Performance in a Mixed-Format Introductory Computer Information Systems Course,'' \textit{Information Systems Education Journal}, vol.~13 no.~1, pp.~14-22, \datestampYM{2015}{}.}



\EntryGapNoBreak
\href{http://elibrary.worldbank.org/doi/abs/10.1596/1813-9450-6060}
{Klaus Desmet, Ejaz Ghani, Stephen D. O'Connell and Esteban Rossi-Hansberg,
``The Spatial Development of India,''
\textit{Journal of Regional Science},
vol.~55,
no.~1,
pp.~10--30,
\DatestampYM{2015}{}.}

\EntryGapNoBreak

\href{http://www.stephenoconnell.org/files/GKO_ReservationsEntry.pdf}
{Ejaz Ghani, William R. Kerr, and Stephen D. O'Connell,
``Political Reservations and Women's Entrepreneurship in India,''
\textit{Journal of Development Economics},
vol.~108,
pp.~138--153,
\DatestampYM{2014}{}.}


\EntryGapNoBreak

\href{http://www.stephenoconnell.org/files/Ghani_Kerr_OConnell_JEG13.pdf}
{Ejaz Ghani, William R. Kerr, and Stephen D. O'Connell,
``Local Industrial Structures and Female Entrepreneurship in India,''
\textit{Journal of Economic Geography},
vol.~13,
no.~6,
pp.~929--964,
\DatestampYM{2013}{}.}

\EntryGapNoBreak

\href{http://www.stephenoconnell.org/files/Ghani_Kerr_OConnell_RS_2013.pdf}
{Ejaz Ghani, William R. Kerr, and Stephen D. O'Connell,
``Spatial Determinants of Entrepreneurship in India,''
\textit{Regional Studies},
vol.~48,
no.~6,
\DatestampYM{2013}{} (special issue).} 

 

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEACHING & PROFESSIONAL EXPERIENCE  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Teaching}
{Teaching}
{PDF:Teaching}

\textbf{Emory University},
Atlanta, GA, USA
\par
Labor Economics (Graduate)
\hfill
Spring 2019

Econometrics I
\hfill
Fall 2019 -        


\par
Honors Thesis Seminar
\hfill
Annual (Fall)

\par
Economics Honors Program Coordinator
\hfill
Since \DatestampYMD{2018}{08}{}

\smallskip
\smallskip


\textbf{Pontificia Universidad Javeriana, Bogot\'{a}},
Bogot\'{a}, D.C., Colombia
\par
Behavioral Economics
\hfill
\DatestampYMD{2016}{06}{}

\smallskip
\smallskip

\textbf{Hunter College, City University of New York},
New York, NY, USA
\par
Econometrics I
\hfill
\DatestampYMD{2011}{08}{} --
\DatestampYMD{2014}{05}{}
\par
Economic Development
\hfill
\DatestampYMD{2012}{08}{} --
\DatestampYMD{2012}{12}{}
\par
Advisor, Senior Honors Thesis (2 students)
\hfill
\DatestampYMD{2013}{01}{} --
\DatestampYMD{2013}{05}{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SEMINAR & CONFERENCE PRESENTATIONS  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Seminars and conferences}
{Seminars}
{PDF:Seminars}
\par
2019: Brigham Young University, UGA, William \& Mary, Georgia Tech ``Challenges in Development'', Western Economics Association. 2018: Emory University. 2017: APPAM; SEA; NEUDC; The World Bank; EPED; Secretaria Especial do Assuntos Estrat\'{e}gicos, Presid\^{e}ncia da Rep\'{u}blica (Brasil); Minist\'{e}rio da Ind\'{u}stria, Com\'{e}rcio Exterior e Servi\c{c}os (Brasil). 2016: Oklahoma State University, Univ. Javeriana Bogot\'{a}, IFPRI, Banco de la Republica (Colombia), NEUDC, Trinity University. 2015: Univ. of California, Riverside, IZA/World Bank Conference on Employment and Development, Univ. of Cologne, The World Bank, DEVPEC, Cornell Dyson GSA, APPAM. 2014 and previous: NEUDC, Universidad de los Andes, NYSEA 2012, MEA 2012.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL REVIEW ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section
{Professional Service}
{Review}
{PDF:Review}
\par Referee: Review of Economics and Statistics*, American Economic Journal: Economic Policy*, European Economic Review, Journal of Development Economics, World Development, Journal of Environmental Economics and Management, Economics of Education Review, Economic Development and Cultural Change, Journal of Regional Science, Journal of Economic Geography*, Regional Studies, Journal of Comparative Economics, Journal of Economic Education, Spatial Economic Analysis. Other review: NSF SBS (Economics) Grant Review, World Bank KCP Program Grant Review, World Bank Development Impact/i2i Grant Program, DFID-IZA Growth in Labor Markets Research Grant Program, Oxford University Press. * indicates multiple.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% GRANTS & AWARDS AND HONORS  %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section
{Grants\newline
\& Awards}
{Grants \& Awards}
{PDF:GrantsAwards}
\par
\BulletItem
The World Bank/ComPEL, \$25,000. Co-PI with Andreas Menzel (CERGE-EI). April 2017.
\BulletItem
PSC CUNY Research Grant, \$3,500. Co-PI. June 2015.
\BulletItem
National Science Foundation Graduate Research Fellowship Program--2012 Honorable Mention
\BulletItem
World Bank 2012 Finance and Private Sector Development (FPD) Academy Award: ``Local Industrial Structures and Female Entrepreneurship in India''
\BulletItem
U.S. Department of Labor Employment and Training Administration, 2011 Employment and Training Research Paper Program. Contract \# DOLJ111A21738, with Yevgeniya Savchenko.
\BulletItem
Merit Scholarship, CUNY Graduate Center Department of Economics, 2011-2012.
\BulletItem
Chancellor's Fellowship, City University of New York, 2010-2015.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}


\textbf{The World Bank},
Washington, DC, USA
\par
Lead Specialist/Principal Investigator (occasional)
\hfill
\DatestampYMD{2016}{05}{} -- 
\DatestampYMD{2018}{06}{}

\smallskip


\par
Consultant (occasional)
\hfill
\DatestampYMD{2010}{01}{} -- 
\DatestampYMD{2016}{05}{}

\smallskip

\textbf{Compass-Lexecon},
Washington, DC, USA
\par
Analyst
\hfill
\DatestampYMD{2007}{06}{} --
\DatestampYMD{2010}{01}{}


%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

English: native; Spanish: conversational (speaking, reading, writing).

\newpage 

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\end{body}

\label{LastPage}~
\end{document}